A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-18 MSRChallenge2016.tex
Minor changes

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{Singapore Management University}\\
       \affaddr{Singapore}\\
       \email{ferdiant.2013@smu.edu.sg}
% 2nd. author
\alignauthor Chu-Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{chupanw@cs.cmu.edu}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
\affaddr{Singapore Management University}\\
\affaddr{Singapore}\\
\email{davidlo@smu.edu.sg}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

We did our analysis on the \emph{2015 September/Github} dataset on Boa. This
dataset includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
revisions. We hope that this population is big enough to reflect the bug fixing
practice.

@@

Table~\ref{tbl:new} shows our analysis results. This table shows that
introducing new classes and new variables are rare. This is good news for
automatic program repair approaches. On average, we still have $0.69$ new method
per bug fix. If we consider the possibility of creating new test method (i.e.
methods that annotated by @Test if JUnit is used), this number is not that
scary. However, what surprises us is that $1.32$ fields are created per bug fix.
This indicates that automatic program repair approaches should pay attention to
the state of the class when fixing Java programs.

\begin{table}
\centering
  \begin{tabular}{| c | r | r |}
  \hline
  Introducing & Total Number & Average \\ \hline \hline
  Class & 729,201 & 0.16 \\ \hline
  Methods & 3,186,867 & 0.69 \\ \hline
  Fields & 6,076,646 & 1.32 \\ \hline
  Variables & 924,259 & 0.2 \\ \hline
  \end{tabular}
  \caption{Introducing new classes, methods, fields, variables to fix bugs}
  \label{tbl:new}
\end{table}

@@

\subsection{What changes are common in real-world bug fixes?}

@@

\begin{table}[!htb]
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
	\centering
	\begin{tabular}{lr} 
		\hline
		& \textbf{GitHub}\\
		\hline
		\#Buggy Files & 46,301,429 \\ 
		\#AMP Pattern & 901,083 \\
		\#MSM Pattern & 783,073 \\
		\#COM Pattern & 270,128 \\ 
		\#CBC Pattern & 1,959,377 \\  
		\#IAO Pattern & 1,308,006 \\  
		\#ANC Pattern & 1,340,561 \\  
		\#AOB Pattern & 128,016 \\  
		\#COB Pattern & 262,915 \\   
		\hline
	\end{tabular}
\end{table}

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{Singapore Management University}\\
       \affaddr{Singapore}\\
       \email{ferdiant.2013@smu.edu.sg}
% 2nd. author
\alignauthor Chu-Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
\affaddr{Singapore Management University}\\
\affaddr{Singapore}\\
\email{davidlo@smu.edu.sg}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

We performed our analysis on the \emph{2015 September/Github} dataset provided by~\cite{dyer2013}. This
dataset includes $7,830,023$ Java projects with $23,229,406$ revisions. Among
all the revisions, $4,590,679$ revisions are identified by Boa as bug fixing
revisions. We hope that this population is big enough to reflect the bug fixing
practice.

@@

Table~\ref{tbl:new} shows our analysis results. This table shows that
introducing new classes and new variables are rare. This is good news for
automatic program repair approaches. On average, we still have $0.69$ new method
per bug fix. If we consider the possibility of creating new test method (i.e.
methods that annotated by @Test if JUnit is used), this number is not that
scary. However, something to notice is that $1.32$ fields are created per bug fix.
This indicates that automatic program repair approaches should pay attention to
the state of the class when fixing Java programs.

\begin{table}
\centering
  \begin{tabular}{| c | r | r |}
  \hline
  Introducing & Total Number & Average \\ \hline \hline
  Class & 729201 & 0.16 \\ \hline
  Methods & 3186867 & 0.69 \\ \hline
  Fields & 6076646 & 1.32 \\ \hline
  Variables & 924259 & 0.2 \\ \hline
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:new}
\end{table}

@@

\subsection{Statement level changes}

@@

\begin{table}[!htb]
	\centering
	\begin{tabular}{lr} 
		\hline
		& \textbf{GitHub}\\
		\hline
		\#Buggy Files & 46,301,429 \\ 
		\#AMP Pattern & 901,083 \\
		\#MSM Pattern & 783,073 \\
		\#COM Pattern & 270,128 \\ 
		\#CBC Pattern & 1,959,377 \\  
		\#IAO Pattern & 1,308,006 \\  
		\#ANC Pattern & 1,340,561 \\  
		\#AOB Pattern & 128,016 \\  
		\#COB Pattern & 262,915 \\   
		\hline
	\end{tabular}
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}

\end{table}
